Declarative Pearl: Lightweight Probabilistic Programming in Curry

### 2015-08-13 Paper/paper.tex
Make progress on draft

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
]{llncs}
% \usepackage[german]{babel}
\title{Declarative Pearl: Lightweight Probabilistic Programming in Curry}
\author{Sandra Dylus}
\institute{Institut f\"ur Informatik, Christian-Albrechts-Universi\"at zu Kiel\\\email{sad@informatik.uni-kiel.de}}
\begin{document}
\maketitle

@@

@@

  Such a filter is often called \emph{partial identity} and a common
  functional logic design pattern \cite{funcLogPattern}, additionaly,
  it corresponds to notion of \emph{observing} a probabilistic value
  and is a standard primitive in probabilistic programming
  languages. %

@@

>>>>

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
]{llncs}
% \usepackage[german]{babel}
\title{Declarative Pearl: Lightweight Probabilistic Programming in Curry}
\author{Sandra Dylus}
\institute{Institut f\"ur Informatik, Christian-Albrechts-Universi\"at zu Kiel\\\email{sad@informatik.uni-kiel.de}}

\newcommand{\code}[1]{{\texttt{#1}}}

\begin{document}
\maketitle

@@

  Rules with overlapping patterns on the left-hand side are one way to
  define nondeterministic functions in Curry. %
  Alternatively, Curry provides an explicite choice operator \code{?}
  that chooses nondeterministic between its first and second
  argument. %

@@

  Such a filter is often called \emph{partial identity} and a common
  functional logic design pattern \cite{funcLogPattern}, additionaly,
  it corresponds to notion of observing a probabilistic value and is a
  standard primitive in probabilistic programming languages. %

@@

\item The choice-operator comes in handy to simplify the corresponding
  search tree. %
  This benefit becomes more clear with the following code examples. %

\begin{verbatim}
coin' = (True, 0.5) ? (False, 0.5)

coin = (True ? False, 0.5)
\end{verbatim}

  There is no semantic difference between the first and second
  definition, however, the corresponding search trees indeed differ. %

  Choice (True, 0.5) (False, 0.5)\\%
  (Choice True False, 0.5)\\%

  The definition of \code{coin'} consists of an expression with a
  nondeterminstic choice on top-level position, whereas the definition
  of \cote{coin} generalises the common parts of the two possible
  values and uses the nondeterminism in a deeper position. %
